\subsection{Authentication Endpoint Context (ae)}
Authenticated endpoints represent peers of IKE connections. Multiple IKE SAs can be established to the same same authenticated endpoint.
\subsubsection{States} ~\\
\begin{contextstates}{Authentication Endpoint Context States}
clean* & Initial clean state. \\
invalid & Error state. \\
stale & AE context is stale. \\
unauth & AE context is unauthenticated. \\
loc\_auth & Local identity of AE is authenticated. \\
rem\_auth & Remote identity of AE is authenticated. \\
authenticated & AE is authenticated. \\
active & AE is authenticated and in use. \\
\end{contextstates}
\subsubsection{Transitions}
\begin{contexttransitions}{Authentication Endpoint Context Transitions}
create &clean& unauth & Create new authenticated endpoint. \\
\tabucline[0.4pt on 0.4pt off 2pt]{-}
sign &unauth& loc\_auth & Sign local authentication octets. \\
\tabucline[0.4pt on 0.4pt off 2pt]{-}
authenticate &loc\_auth& authenticated & Verify remote authentication octets. \\
\tabucline[0.4pt on 0.4pt off 2pt]{-}
activate &authenticated& active & Use authenticated endpoint for IKE SA. \\
\tabucline[0.4pt on 0.4pt off 2pt]{-}
is\_initiator &active \newline authenticated \newline loc\_auth \newline rem\_auth \newline unauth& active & Return local initiator role of authenticated endpoint. \\
\tabucline[0.4pt on 0.4pt off 2pt]{-}
get\_nonce\_rem &active \newline authenticated \newline loc\_auth \newline rem\_auth \newline unauth& active & Return nonce of remote peer. \\
\tabucline[0.4pt on 0.4pt off 2pt]{-}
get\_nonce\_loc &active \newline authenticated \newline loc\_auth \newline rem\_auth \newline unauth& active & Return local nonce. \\
\tabucline[0.4pt on 0.4pt off 2pt]{-}
get\_sk\_ike\_auth\_loc &active \newline authenticated \newline loc\_auth \newline rem\_auth \newline unauth& active & Return local SK\_p value. \\
\tabucline[0.4pt on 0.4pt off 2pt]{-}
get\_sk\_ike\_auth\_rem &active \newline authenticated \newline loc\_auth \newline rem\_auth \newline unauth& active & Return remote SK\_p value. \\
\tabucline[0.4pt on 0.4pt off 2pt]{-}
reset &*& clean & Reset authenticated endpoint to initial clean state. \\
\tabucline[0.4pt on 0.4pt off 2pt]{-}
invalidate &*& invalid & Invalidate authenticated endpoint; it can only be reused by explicitly resetting the context. \\
\end{contexttransitions}